---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rUrgAra

<!-- badges: start -->
[![R-CMD-check](https://github.com/CC-URGARA/rUrgAra/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/CC-URGARA/rUrgAra/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

rUrgAra is an internal package to Urg'Ara. It helps garanty uniformity and ease of implementation of recurrent tasks performed in the company as well as the implementation of Urg'Ara's graphical chart. 

## Installation

You can install the development version of rUrgAra from [GitHub](https://github.com/) with:

```{r, eval = F}
# install.packages("devtools")
devtools::install_github("https://github.com/CC-URGARA/rUrgAra", build_vignettes = T)
```

## Example

Exemples of use are available in the "Getting started" vignette

```{r, eval = F}
vignette("Getting started", package = "rUrgAra")
```

