---
title: "Getting-started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rUrgAra)
```

# Exemple dataset

We will see in this vignette how rUrgAra can help in plotting charge diagram and graphs following rUrgAra's graphical chart.


# Plot a charge diagram

This exemple shows how to plot a charge diagram using rUrgAra's plot_diag_charge() from a table containing entry and exit date/times.


```{r example-plot_diag_charge, fig.width = 10, fig.height = 7}
#Table of entry/exit times
head(df_ex_charge)
#Charge diagram with exclusion of patients staying more than 3 days (72*60 = 4320 minutes)
# not taking into account strata 
list_charge = plot_diag_charge(data = df_ex_charge, entry = "ENTREE",
                               exit = "SORTIE", max_LOS = 72*60)
#plot_diag_charge return two objects, a table showing for each hour of
# the day how many patient came from what hour (-1 = day before)
head(list_charge$tab)
#a charge diagram
list_charge$plot

#adding a strata to take into account that data are coming from two hospitals
list_charge_stratified = plot_diag_charge(data = df_ex_charge, entry = "ENTREE",
                                          exit = "SORTIE", strata = "Etablissement",
                                          max_LOS = 72*60)
#plot_diag_charge return two objects, a table showing for each hour of
# the day how many patient came from what hour (-1 = day before)
head(list_charge_stratified$tab)
#a charge diagram
list_charge_stratified$plot

#Limiting the charge diagram to a set period
list_charge_stratified = plot_diag_charge(data = df_ex_charge, entry = "ENTREE",
                                          exit = "SORTIE", strata = "Etablissement",
                                          from = "10/01/2022", to = "20/01/2022",
                                          max_LOS = 72*60)
list_charge_stratified$plot + 
  ggplot2::labs(title = "From 10/01/2022 to 20/01/2022")

#Hiding the number of entry/exit
list_charge_no_lines = plot_diag_charge(data = df_ex_charge, entry = "ENTREE",
                                          exit = "SORTIE", strata = "Etablissement",
                                          show_lines = FALSE)
list_charge_no_lines$plot
```

# Adding a company logo to a plot

This exemple shows how to add a company logo (by default UrgAra's) to a ggplot object.


```{r example-plot_add_logo, fig.width = 10, fig.height = 7}
plot_cars = ggplot2::ggplot(cars, ggplot2::aes(x = speed, y = dist)) +
  ggplot2::geom_point() +
  ggpubr::theme_pubclean()

plot_add_logo(plot_cars)#default
plot_add_logo(plot_cars, position = "top left")#logo at the top
plot_add_logo(plot_cars, width = 0.4)#wider logo
```

# Adding rUrgAra color palette

## Applying rUrgAra palette to a color scale

```{r, fig.width = 10, fig.height = 7}
plot_iris = ggplot2::ggplot(iris, ggplot2::aes(x = Sepal.Length, y =  Sepal.Width, color = Species)) +
  ggplot2::geom_point(size = 1.5)

plot_iris#default

plot_iris +
  ggplot2::scale_color_manual(values = pal_UrgAra()) +#Urg'Ara's color palette
  ggpubr::theme_pubclean() +
  ggplot2::theme(legend.key = ggplot2::element_blank())
```


## Applying rUrgAra palette to a fill scale

```{r, fig.width = 10, fig.height = 7}
plot_iris_bar = ggplot2::ggplot(iris, ggplot2::aes(x = Sepal.Length, y =  Sepal.Width, fill = Species)) +
  ggplot2::geom_col()

plot_iris_bar#default

plot_iris_bar +
  ggplot2::scale_fill_manual(values = pal_UrgAra()) +#Urg'Ara's color palette
  ggpubr::theme_pubclean()
```


## Applying rUrgAra palette to a dichotomous variable

```{r, fig.width = 10, fig.height = 7}
plot_iris_dicho = ggplot2::ggplot(iris, ggplot2::aes(x = 1, y =  Sepal.Width, fill = Sepal.Length > 5)) +
  ggplot2::geom_col()

plot_iris_dicho#default

plot_iris_dicho +
  ggplot2::scale_fill_manual(values = pal_UrgAra(palette = "duo")) +#Urg'Ara's color palette
  ggpubr::theme_pubclean()
```


## Importing templates from rUrgAra

You can import a template from rUrgAra using get_template

```{r, eval = F}
get_template(template_name = "report", folder = "src/")
```


